%!TEX program = xelatex

\documentclass{cls/simplecv}


\begin{document}

\name{LIN Hao}
\contact{\phone ~138 1234 5678  \quad \mail~ linhao@email.com }

\maketitle

\section{Summary}

\textbf{This content is entirely fictional and is only used to demonstrate the resume template.}

\begin{enumerate}
	\item Senior full-stack engineer with 7 years of experience in AI and distributed systems R\&D. 
	\item Proficient in Python/Java tech stacks, led the deployment of 3 AI products serving millions of users, and excels in deep learning model optimization and high-concurrency microservice architecture design.
	\item Winner of the ACM International Programming Competition Asia Gold Award, published 5 IEEE/SCI papers, and holds 6 technical patents.
	\item Strong capability in tackling technical challenges from scratch and cross-department collaboration, adept at translating academic research into industrial solutions.
\end{enumerate}

\section{Projects}

\textbf{2022.03 -- 2023.06 \quad Deep Learning-Based Remote Sensing Image Classification System}
\begin{itemize}
	\item Tech Stack: PyTorch/OpenCV/Django
	\item Developed a ResNet-Transformer hybrid model, achieving 98.2\% accuracy in farmland recognition
	\item Designed a multi-threaded data preprocessing pipeline, improving training efficiency by 300\%
	\item Won the Best Application Innovation Award at the 2023 China AI Conference
\end{itemize}

\textbf{2020.09 -- 2022.02 \quad Distributed E-Commerce Recommendation System Overhaul}
\begin{itemize}
	\item Tech Stack: Spring Cloud/Redis/Flink
	\item Refactored monolithic architecture, increasing QPS from 1,500 to 12,000+
	\item Implemented real-time user profile updates, boosting recommendation conversion by 27\%
\end{itemize}

\textbf{2019.01 -- 2020.06 \quad Medical Knowledge Graph Visualization Platform}
\begin{itemize}
	\item Tech Stack: Neo4j/React/D3.js
	\item Built a medical knowledge graph containing 5.3 million entity relationships
	\item Developed a dynamic relationship discovery algorithm, improving diagnostic efficiency by 40\%
\end{itemize}

\section{Education}

\begin{tabular}{llll}
	2023.07 -- 2020.06 & Ph.D. & Federated Learning & Tsinghua University \\
	2014.09 -- 2017.06 & M.S. & Distributed Computing & Zhejiang University\\
	2010.09 -- 2014.06 & B.S. & Computer Science & Nanjing University
\end{tabular}

\section{Work Experience}
\begin{tabular}{lll}
	2023.07 -- Present & Principal AI Engineer / AutoML Toolchain & Microsoft Research Asia \\
	2020.07 -- 2023.06 & Senior R\&D Engineer / Recom. Algorithms & Alibaba DAMO Academy\\
	2017.07 -- 2020.06 & Full-Stack Developer / Recom. System & Byte Dance\\
\end{tabular}

\section{Skills}

\begin{description}
	\item[Languages]  Expert in Python; Proficient in Java/C++; Skilled in Shell/Git
	\item[Frameworks] TensorFlow/Kubernetes/Spark
	\item[Tools] GitLab CI/CD/Elasticsearch/Airflow
	\item[Domains] Machine Learning System Design/Cloud-Native Architecture/Performance Optimization
\end{description}

\section{Patents}

[1] "Multimodal Fusion-Based Intelligent Customer Service Dialogue System" (ZL202310123456.7) 2023.05

[2] "Blockchain-Powered Supply Chain Traceability Method" (ZL202210654321.1) 2022.11

[3] "Collaborative Path Planning Algorithm for UAV Swarms" (ZL202180765432.9) 2021.09


\section{Publications}
[1] Hao Lin. \emph{Federated Learning with Adaptive Differential Privacy}
IEEE TPAMI (IF=24.314), 2023.04.

[2] Hao Lin. \emph{Dynamic Graph Convolution for 3D Point Cloud Segmentation}. CVPR 2022 Oral.

[3] Hao Lin. \emph{A Survey of Edge Computing Architectures}. ACM Computing Surveys, 2020.12.


\end{document}